No Replication Without Process Documentation:  An Assessment of Management

### 2020-04-06 R/MSE manuscript.Rmd
Edit search methods

# Methods 
## Finding and Sampling the MSE Literature 
We conducted our search for MSEs in the SCI-EXPANDED index from Web of Science, searching for “management strategy evaluation” by topic across all years on January 8th, 2019. This search returned 264 results.  We reviewed a random sample of 30 articles that document a MSE (supplement 2), removing articles that were reviews, meta-analyses, or simply cited other MSE articles from our sample. After removing other articles from the original set of 264 articles, 154 articles document a MSE.  We reviewed 16 climate change MSE articles (supplement 2). Twelve of these articles came from our original search.  To give as full a picture of the climate change MSE articles to date as possible we also reviewed the 4 additional climate change MSE articles published in 2019.

| MSE type | Count |
|:--:|:--:|
| Published | 154 |
| Random Sample | 30 |
| Climate Change | 12 |

>>>>

# Methods 
## Finding and Sampling the MSE Literature 
We conducted our search for MSEs in the SCI-EXPANDED index from Web of Science, searching for “management strategy evaluation” by topic across all years on January 8th, 2019 (Table 1). This search returned 264 results.  We reviewed a random sample of 30 articles that document a MSE (supplement 2), removing articles that were reviews, meta-analyses, or simply cited other MSE articles from our sample. After removing other articles from the original set of 264 articles, 154 articles document a MSE.  We reviewed 16 climate change MSE articles (supplement 2). Twelve of these articles came from our original January 8th, 2019 Web of Science search.  To give as full a picture of the climate change MSE articles to date as possible we also reviewed the 4 climate change MSE articles published in 2019.

Table 1. Januaray 8, 2019 Web of Science "management strategy evaluation" search results
| MSE type | Count |
|:--:|:--:|
| Published | 154 |
| Random Sample | 30 |
| Climate Change | 12* |  
* We also reviewed 4 additional climate change MSE articles published in 2019 for a total of 16.
